### 2023-10-17 doc/Thesis/chapter/01-introduction.tex
corrected until comp details

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Photovoltaics (PV) is one viable option when becoming carbon neutral. 
Furthermore, 
it uses the sun's energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search} which harness the whole power output of the sun.
%
One sort of PV are CIGS (copper indium gallium sulfide) cells\cite{Vasekar2010}. 
Due to their large absorption coefficient, less material is needed and they can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple cells are operated in series. 
The cells must be applied to a non-conducting surface.
Glass is a good non-conducting substrate, but very rigid and brittle. 
An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be synthesised on top.
Polymere would be a obvious choice if not for its low melting point which makes high prodction temperatures inpractical.
A non-toxic material which is suitable for the insulation is \ch{ZrO2}. 
An economic and scalable method is doctor blading via a sol-gel process. 
Sol-gel processes often produce porous layers. 
In this work a dense, insulating and homogeneous layer is pursued. 
Machine learning can help to uncover complex non-linear relations, such as the 
dependence of the thickness and resistance of the resulting layer on production factors.
%\td{influence} of the production factors on the thickness and resistance of the resulting layer.
The minimization of the conductance is performed with a particle swarm optimization 
algorithm. 
%The resulting optimum is compared with other optimization methods.

@@

The remainder of this work is organized with chapter 
%\ref{sec:aims} providing insight into the motivation and the goals. Section \ref{sec:theoretical} gives
\ref{sec:theoretical} giving 
some background information on topics of PV, material science and computational science which were used in this work.
In chapter \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
Section \ref{sec:results} is split into three sections: material specific results are presented in section \ref{sec:res-mat}, results regarding particle swarm optimization in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
Finally, chapter \ref{sec:outlook} summarizes and discusses the outlook and next steps.

>>>>

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Photovoltaics (PV) is one viable option for becoming carbon neutral. 
Furthermore, 
it uses the sun's energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search} which harness the whole power output of the sun.
%
One sort of PV are CIGS (copper indium gallium sulfide) cells\cite{Vasekar2010}. 
Due to their large absorption coefficient (compared to silicon based cells), less material is needed and they can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple cells are operated in series. 
The cells must be applied to a non-conducting surface.
Glass is a good non-conducting substrate, but very rigid and brittle. 
An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be synthesised on top.
Polymere would be a obvious choice if not for its low melting point which makes high prodction temperatures inpractical.
A non-toxic material which is suitable for the insulation is \ch{ZrO2}. 
An economic and scalable method is doctor blading via a sol-gel process. 
Sol-gel processes often produce porous layers. 
In this work a dense, insulating and homogeneous layer is pursued. 
Machine learning can help to uncover complex non-linear relations, such as the 
dependence of the thickness and resistance of the resulting layer on production factors.
%\td{influence} of the production factors on the thickness and resistance of the resulting layer.
The minimization of the conductance of the layer is performed with a particle swarm optimization 
algorithm. 
%The resulting optimum is compared with other optimization methods.

@@

The remainder of this work is organized with chapter 
%\ref{sec:aims} providing insight into the motivation and the goals. Section \ref{sec:theoretical} gives
\ref{sec:theoretical} giving 
some background information on topics of PV, material science and computational science which were used in this work.
In chapter \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
Section \ref{sec:results} is split into four sections: material specific results are presented in section \ref{sec:res-mat}, results regarding particle swarm optimization in section \ref{sec:res-emma}, further analysis in section \ref{sec:res-post-emma} and discussion of the process and the results in \ref{sec:res-discussion}.
Finally, chapter \ref{sec:outlook} summarizes and discusses the outlook and next steps.

### 2023-10-17 doc/Thesis/chapter/030-theory-materials.tex
corrected until comp details

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Photovoltaics Basics}
The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
the creation of an electron-hole pair and then its separation by the structure of the material\cite{markvart2013principles}.
This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. 
This is often achieved through a p-n junction.
The n-type side has excess electrons and p-type side has excess electron holes. 
If the n- and p-type are of the same basis material, they are called homojunctions (e.g. silicon); if not, heterojunctions e.g. \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe}\cite{breitenstein2013understanding}.
%
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still 
have the biggest market share in the \gls{pv} segment (including polycrystalline and monocrystalline silicon).
In 2022 
over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon)\cite{breitenstein2013understanding}.
%
A comprehensive overview on different \gls{pv} technologies can be found in \cite{markvart2013principles}.

@@

Amazingly, the band gap of CIGS can be varied between \ev{1} and \ev{1.7} by varying the indium gallium ratio.
This is a result of the large difference of band gaps of \ch{CuInSe2} and \ch{CuGaSe2} (see table \ref{tab:cigs}). 
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In figure \ref{fig:cigs} the schematic layer sequence of a standard \gls{cigs} thin film cell is shown. 
Typically a \um{1} thick molybdenum layer is deposited on soda lime glass. 
The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in 112 direction\cite{hedstrom1993cigs}.
A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporation from elemental sources controlled by a mass spectrometer.\cite{hedstrom1993cigs}
The p-type doping of \gls{cigs} is achieved by adding more than stoichiometric copper to the mix. 
The heterojunction is then completed by deposition of \ch{CdS} (typically \nm{50} thick).
\ch{CdS} was earlier used as front contact, but now only acts as n-type wide-gap window and buffer. 
\ch{ZnO} has a band gap of \ev{3.2} and is therefore transparent for visible light. 
The \ch{ZnO} window layer (usually of thickness 50-\nm{70} is highly conductive (especially the \ch{Al} doped layer) and acts as front contact.

%
Instead of glass as substrate, steel and plastics (e.g. polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
They both come with their own inconveniences. 
Plastics generally have very low melting points which restrict preparation temperatures.
Steel, on the other hand, is temperature resistant enough, but is an electric conductor. 
The conductance of steel can be masked by a insulator layer (e.g. \ch{ZrO2}, \ch{Al2O3}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sol-Gel and Doctor Blading}
%\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
%
\Gls{db} coating (also known as tape casting) is widely used in the textile, paper, photographic film, printing and ceramic industries.
The roll-to-roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed velocity.
In roll-to-roll processes the substrate moves instead of the blade.

@@

\pagebreak[4]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   SEM    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scanning electron Microscopy}
The history of \gls{sem} can be traced back to 1843 when Scottish clockmaker Alexander Bain filed a patent for dissecting an image by scanning. 
The first \gls{sem} was build in 1933, 
the first images from scanning electron beams were published in 1935
and the first \gls{sem} was marketed in 1965.
A more detailed history of \gls{sem} can be read in a open-to-read paper by McMullan from 1995\cite{McMullan1995}. 
\Gls{sem} is a microscopical technique which allows visualization of surfaces with features in the nano meter regime. 
While optical microscopes use visible light and optical lenses, \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to visible light\cite{Kaliva2020}.
The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons in the examined material. 
Secondary electrons carry information to conclude morphology and topology of the sample while X-rays can be used to identify the elements. 
Electrons originate from either a \gls{feg}, where a strong electrical field rips electrons from the bulk, or from thermionic guns where a filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted. 
Electrons are then accelerated by a voltage of \SI{2}{\kilo\volt} to \SI{40}{\kilo\volt} and bundled into narrow beams by lenses\cite{Vernon2000}.
A high mean free path is needed for electrons to travel from the source to the sample (and to the detector). 
Thus, a very low pressure is needed inside the microscope. 
In this work \gls{sem} was used as a preliminary way of checking the quality of \gls{zro} layer. 
% squeeze condition into this page 
\enlargethispage{\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{UV/Vis/NIR Spectroscopy}
%%% WHAT? 
\Gls{uv}/\gls{vis}/\gls{nir} spectroscopy is a molecular spectroscopic method using 
interactions of \gls{uv}, \gls{vis} and \gls{nir} light 
(wavelengths of \num{e-7} to \num{e-6}\m{}) with molecules\cite{Schwedt2008}.
In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$)\cite{gHobel2006international}.
In other materials light moves with the velocity $v=\frac{c}{n(\lambda)}$, where $n(\lambda)$
is the refractive index which is dependent on the wavelength $\lambda$. 
%is the refractive index which is a function of the wavelength $\lambda$. 
The relation of the energy of a photon~$E$, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges; % (\td{see figure?+table});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
%Molecular vibrations can be separated in valence and deformation vibrations.
%
% UVVis
Two prerequisites need to be fulfilled in order for a \gls{uv}\gls{vis} photon to be 
absorbed by a molecule or atom.
Firstly, the energy must be the same as the difference between two electronic states, a lower populated and a higher empty orbital. 
The electron will then be excited into a energetically higher orbital.
Secondly, the spin state of both states has to be the same otherwise the transition is "forbidden" and the absorption is extremely unlikely.

% IR
\Gls{ir} photons interact with molecular vibrations, which is only a part of the degrees of freedom of a molecule.
A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
%
The number of vibrations can therefore be calculated as 
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active. 
The absorption of \Gls{nir} electromagnetic waves involves excitations of non-fundamental vibrations, overtones and combination modes which lead to intricate patterns called the fingerprint region. 
These transition are mostly "forbidden" quantum mechanically and allow analysis of bulk matter without extensive preparation
due to the deep penetration depth of \gls{nir} light\cite{bec2019breakthrough}.

@@

\subsubsection{Fourier Transform Spectrometer}
 %A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
In the classic two-beam-spectrometer the light emitted from the light source is split, 
sent through the sample and the reference and one of the two beams is alternately 
sent through a monochromator to a detector (often a thermopile).
%
In the \gls{ft} spectrometer the beam is sent through the sample, split and 
reflected from a static and from a moving mirror, recombined and detected by a photo 
multiplier (a device which transforms photons into electrical signals). 
How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams\cite{Schwedt2008}.
In a \gls{ft} spectrometer the reference has to be measured before the sample.
%
%When the refractive index of two layers differ, light can be used to measure the thickness\cite{Dumin1967} of the optical less dense material.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Photovoltaics Basics}
The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in human made \gls{pv} or in plants): 
the creation of an electron-hole pair and then its separation by the structure of the material\cite{markvart2013principles}.
This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. 
This is often achieved through a p-n junction.
The n-type side has excess electrons and p-type side has excess electron holes. 
If the n- and p-type are of the same basis material, they are called homojunctions (e.g. silicon); if not, heterojunctions e.g. \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe}\cite{breitenstein2013understanding}.
%
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still 
have the biggest market share in the \gls{pv} segment (including polycrystalline and monocrystalline silicon).
In 2022 
over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon)\cite{breitenstein2013understanding}.
%
A comprehensive overview on different \gls{pv} technologies can be found in \cite{markvart2013principles}.

@@

Amazingly, the band gap of CIGS can be varied between \ev{1} and \ev{1.7} by varying the indium gallium ratio.
This is a result of the large difference of band gaps of \ch{CuInSe2} and \ch{CuGaSe2} (see table \ref{tab:cigs}). 
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In figure \ref{fig:cigs} the schematic layer sequence of a standard \gls{cigs} thin film cell is shown. 
Typically, a \um{1} thick molybdenum layer is deposited on soda lime glass. 
The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in 112 direction\cite{hedstrom1993cigs}.
A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporation from elemental sources controlled by a mass spectrometer.\cite{hedstrom1993cigs}
The p-type doping of \gls{cigs} is achieved by adding more than stoichiometric copper to the mix. 
The heterojunction is then completed by deposition of \ch{CdS} (typically \nm{50} thick).
\ch{CdS} was earlier used as front contact, but now only acts as n-type wide-gap window and buffer. 
\ch{ZnO} has a band gap of \ev{3.2} and is therefore transparent for visible light. 
The \ch{ZnO} window layer (usually of thickness 50-\nm{70} is highly conductive (especially the aluminium doped layer) and acts as front contact.

%
Instead of glass as substrate, steel and plastics (e.g. polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
They both come with their own inconveniences. 
Plastics generally have very low melting points which restrict preparation temperatures of \gls{cigs}.
Steel, on the other hand, is temperature resistant enough, but is an electric conductor. 
The conductance of steel can be masked by a insulator layer (e.g. \ch{ZrO2}, \ch{Al2O3}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Sol-Gel and Doctor Blading}
\subsection{Doctor Blading}
%\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
%
\Gls{db} coating (also known as tape casting) is widely used in the textile, paper, photographic film, printing and ceramic industries.
The roll-to-roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed velocity.
In roll-to-roll processes the substrate moves instead of the blade.

@@

\pagebreak[4]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   SEM    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scanning electron Microscopy}
The history of \gls{sem} can be traced back to 1843 when Scottish clockmaker Alexander Bain filed a patent for dissecting an image by scanning. 
The first \gls{sem} was build in 1933, 
the first images from scanning electron beams were published in 1935
and the first \gls{sem} was marketed in 1965.
A more detailed history of \gls{sem} can be read in a open-to-read paper by McMullan from 1995\cite{McMullan1995}. 
\Gls{sem} is a microscopical technique which allows visualization of surfaces with features in the nano meter regime. 
While optical microscopes use visible light and optical lenses, \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to photons of visible light\cite{Kaliva2020}.
The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons in the examined material. 
Secondary electrons carry information to conclude morphology and topology of the sample, while X-rays can be used to identify the elements. 
Electrons originate from either a \gls{feg}, where a strong electrical field rips electrons from the bulk, or from thermionic guns where a filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted. 
Electrons are then accelerated by a voltage of \SI{2}{\kilo\volt} to \SI{40}{\kilo\volt} and bundled into narrow beams by lenses\cite{Vernon2000}.
A high mean free path is needed for electrons to travel from the source to the sample (and to the detector). 
Thus, a very low pressure is needed inside the microscope. 
In this work \gls{sem} was used as a preliminary way of checking the quality of \gls{zro} layer. 
% squeeze condition into this page 
\enlargethispage{\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{UV/Vis/NIR Spectroscopy}
%%% WHAT? 
\Gls{uv}/\gls{vis}/\gls{nir} spectroscopy is a molecular spectroscopic method using 
interactions of \gls{uv}/\gls{vis}/\gls{nir} light 
(wavelengths of \num{e-7} to \num{e-6}\m{}) with molecules\cite{Schwedt2008}.
In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$)\cite{gHobel2006international}.
In other materials light moves with the velocity $v=\frac{c}{n(\lambda)}$, where $n(\lambda)$
is the refractive index which is dependent on the wavelength $\lambda$. 
%is the refractive index which is a function of the wavelength $\lambda$. 
The relation of the energy of a photon~$E$, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges; % (\td{see figure?+table});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
%Molecular vibrations can be separated in valence and deformation vibrations.
%
% UVVis
Two prerequisites need to be fulfilled in order for a \gls{uv}\gls{vis} photon to be 
absorbed by a molecule or atom.
Firstly, the energy must be the same as the difference between two electronic states, a lower populated and a higher empty orbital. 
The electron will then be excited into a energetically higher orbital.
Secondly, the spin state of both states has to be the same otherwise the transition is quantum mechanically "forbidden" and the absorption is extremely unlikely.

% IR
\Gls{ir} photons interact with molecular vibrations, which is only a part of the degrees of freedom of a molecule.
A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
%
The number of vibrations can therefore be calculated as 
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active. 
The absorption of \Gls{nir} electromagnetic waves involves excitations of non-fundamental vibrations, overtones and combination modes which lead to intricate patterns in the so called fingerprint region. 
These transition are mostly "forbidden" and allow analysis of bulk matter without extensive preparation
due to the deep penetration depth of \gls{nir} light\cite{bec2019breakthrough}.

@@

\subsubsection{Fourier Transform Spectrometer}
 %A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
In the classic two-beam-spectrometer the light emitted from the light source is split, 
sent through the sample and the reference, and one of the two beams is alternately 
sent through a monochromator to a detector (often a thermopile).
%
In the \gls{ft} spectrometer the beam is sent through the sample, split and 
reflected from a static and from a moving mirror, recombined and detected by a photo 
multiplier (a device which transforms photons into electrical signals). 
How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams\cite{Schwedt2008}.
In a \gls{ft} spectrometer the reference has to be measured before the sample.
%
%When the refractive index of two layers differ, light can be used to measure the thickness\cite{Dumin1967} of the optical less dense material.
